### 2024-08-18 paper.tex
some work on Jordan basis

\end{proof}
Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
We will find the irreducible components of \(U_{I, (\rho_i)}\), and show that their closures are in fact irreducible components of \(U_0\).
\par I claim that \(A_{0,b}\) has the same shape for every \((A_{0, b}, U) \in U_{I, (\rho_i)}\).
Call this shape \(\mu\).
By finding a algebraic map taking \(b\) to a Jordan basis for \(A_{0,b}\), we will put \(U_{I, (\rho_i)}\) in isomorphism with the product (choice of \(b\)) \(\times\) (Springer fiber at \(J(\mu)\)).
Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(U_{I, (\rho_i)}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)

@@

\par TODO: begin Jordan basis thing in earnest here.
\par Normally we index \(e_{ij}\) so that \(\lambda_i\) is nonincreasing with \(i\).
Now, it will be more convenient to assume our indices are such that \(q_i\) is nonincreasing, so we will do that: from now on, we assume that \(q_i\) is nonincreasing.
\par We list the chains of the Jordan basis in (roughly) order of decreasing length.
First, for each \(i\) such that \(q_i \geq n\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).

@@

Let \(P = \max_{i : q_i < n} p_i\).

>>>>

Fix any \(I\) and \((\rho_i)\) satisfying the conditions of Lemma 8.1.
We will find the irreducible components of \(U_{I, (\rho_i)}\), and show that their closures are in fact irreducible components of \(U_0\).
\par I claim that \(A_{0,b}\) has the same shape for every \((A_{0, b}, U) \in U_{I, (\rho_i)}\).
Call this shape \(\mu\).
By finding a algebraic map taking \(b\) to a Jordan basis for \(A_{0,b}\), we will put \(U_{I, (\rho_i)}\) in isomorphism with the product (choice of \(b\)) \(\times\) (Springer fiber at \(J(\mu)\)).
Then we will use our result about the usual Springer fiber at \(J(\mu)\) to find the irreducible components of \(U_{I, (\rho_i)}\).
(I should define this somewhere else, but \(J(\mu)\) just has the blocks in order of nonincreasing size.)

@@

\par So, now we find a Jordan basis for \(A_{0, b}\).
\par We list the chains of the Jordan basis.
First, for each \(i \notin I\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i,p_i + q_i} = e_{i\lambda_i}\)
% First, for each \(i\) such that \(q_i \geq n\), we take the chain of length \(p_i + q_i\) beginning with \(e_{i, p_i + q_i}\).
(Agh, the definition of I was wrong, we also need the the condition relating \(q_i\) to \(n\).)

@@

Let \(P = \max_{i : q_i < n} p_i = (something in terms of \rho)\).
